Wrattler: \textnormal{A platform for AI-assisted data science}

### 2018-03-06 report/paper.tex
Fix latex bugs, generate nice PDF
Minor style tweaks

\usepackage{lineno,hyperref,xcolor}
\usepackage{flushend}
\usepackage{stmaryrd}
\usepackage{amssymb}
\usepackage{xypic}
\usepackage{semantic}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage[shortlabels]{enumerate}
\setlist{leftmargin=6mm}

\newcounter{thc}
\newcounter{dfc}

\theoremstyle{plain}
\newtheorem{lem}[thc]{Lemma}
\newtheorem{theorem}[thc]{Theorem}

\theoremstyle{definition}
\newtheorem{definition}[dfc]{Definition}

@@

\author{Authors}
%\affiliation{
%  \institution{The Alan Turing Institute}
%  \country{London, United Kingdom}
%}
%\email{tomas@tomasp.net}

\definecolor{cmtclr}{rgb}{0.0,0.6,0.0}
\definecolor{kvdclr}{rgb}{0.0,0.0,0.6}
\definecolor{numclr}{rgb}{0.0,0.4,0.0}
\definecolor{strclr}{rgb}{0.4,0.4,0.0}
\definecolor{rstrclr}{rgb}{0.5,0.1,0.0}
\definecolor{prepclr}{rgb}{0.6,0.0,0.2}
\newcommand{\vect}[1]{\langl #1 \rangl}
\newcommand{\langl}{\begin{picture}(4.5,7)
\put(1.1,2.5){\rotatebox{60}{\line(1,0){5.5}}}
\put(1.1,2.5){\rotatebox{300}{\line(1,0){5.5}}}
\end{picture}}
\newcommand{\rangl}{\begin{picture}(4.5,7)
\put(.9,2.5){\rotatebox{120}{\line(1,0){5.5}}}
\put(.9,2.5){\rotatebox{240}{\line(1,0){5.5}}}
\end{picture}}
\newcommand{\ball}[1]{\FPeval{\result}{clip(201+#1)}\textnormal{\ding{\result}}}
\newcommand{\lsep}{~\,|\,~}
\newcommand{\num}[1]{\textcolor{numclr}{#1}}
\newcommand{\str}[1]{\textnormal{\textcolor{strclr}{\sffamily "#1"}}}
\newcommand{\rstr}[1]{\textnormal{\textcolor{rstrclr}{\sffamily "#1"}}}
\newcommand{\ident}[1]{\textnormal{\sffamily #1}}
\newcommand{\qident}[1]{\textnormal{\sffamily \guillemotleft #1\guillemotright}}
\newcommand{\dom}{\ident{dom}}
\newcommand{\kvd}[1]{\textnormal{\textcolor{kvdclr}{\sffamily #1}}}

@@

As an example, consider the following Schema.org description of a place (the following shows a
JSON encoding, but it is worth noting that Schema.org also supports RDF encoding):
%
\begin{equation*}
\begin{array}{l}
\{~~\; \str{@context}: \str{http://schema.org},\\
\quad  \str{@type}: \str{Place},\\
\quad  \str{name}: \str{The Black Lodge},\\
\quad  \str{address}: \{\\
\qquad    \str{@type}: \str{PostalAddress},\\
\qquad    \str{addressLocality}: \str{London},\qquad\qquad\qquad\qquad\qquad~\\
\qquad    \str{postalCode}: \str{NW53HL} ~\}~\}\\
\end{array}
\end{equation*}

\noindent
The \str{@context} attribute defines a namespace of a schema that defines the available
entities. The default namespace, used here, includes two entities that we use in this 
example, namely Place and PostalAddress.

>>>>

\usepackage{lineno,hyperref,xcolor}
\usepackage{flushend}
\usepackage{stmaryrd}
\usepackage{amssymb}
\usepackage{xypic}
\usepackage{semantic}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{enumerate}
\setlist{leftmargin=6mm}

@@

\author{AIDA Team, The Alan Turing Institute}
%\affiliation{
%  \institution{The Alan Turing Institute}
%  \country{London, United Kingdom}
%}
%\email{tomas@tomasp.net}

\definecolor{cmtclr}{rgb}{0.0,0.6,0.0}
\definecolor{kvdclr}{rgb}{0.0,0.0,0.6}
\definecolor{numclr}{rgb}{0.0,0.4,0.0}
\definecolor{strclr}{rgb}{0.4,0.4,0.0}
\definecolor{rstrclr}{rgb}{0.5,0.1,0.0}
\definecolor{prepclr}{rgb}{0.6,0.0,0.2}
\newcommand{\vect}[1]{\langl #1 \rangl}
\newcommand{\langl}{\begin{picture}(4.5,7)
\put(1.1,2.5){\rotatebox{60}{\line(1,0){5.5}}}
\put(1.1,2.5){\rotatebox{300}{\line(1,0){5.5}}}
\end{picture}}
\newcommand{\rangl}{\begin{picture}(4.5,7)
\put(.9,2.5){\rotatebox{120}{\line(1,0){5.5}}}
\put(.9,2.5){\rotatebox{240}{\line(1,0){5.5}}}
\end{picture}}
\newcommand{\ball}[1]{\FPeval{\result}{clip(201+#1)}\textnormal{\ding{\result}}}
\newcommand{\lsep}{~\,|\,~}
\newcommand{\num}[1]{\textcolor{numclr}{#1}}
\newcommand{\str}[1]{\textnormal{\textcolor{strclr}{\sffamily "#1"}}}
\newcommand{\strf}[1]{\textnormal{\textcolor{strclr}{\sffamily #1}}}
\newcommand{\rstr}[1]{\textnormal{\textcolor{rstrclr}{\sffamily "#1"}}}
\newcommand{\ident}[1]{\textnormal{\sffamily #1}}
\newcommand{\qident}[1]{\textnormal{\sffamily \guillemotleft #1\guillemotright}}
\newcommand{\dom}{\ident{dom}}
\newcommand{\kvd}[1]{\textnormal{\textcolor{kvdclr}{\sffamily #1}}}

@@

\begin{figure}
\begin{equation*}
\begin{array}{l}
\{~~\; \str{@context}: \str{http://schema.org},\\
\quad  \str{@type}: \str{Place},\\
\quad  \str{name}: \str{The Black Lodge},\\
\quad  \str{address}: \{\\
\qquad    \str{@type}: \str{PostalAddress},\\
\qquad    \str{addressLocality}: \str{London},\qquad\qquad\qquad\qquad\qquad~\\
\qquad    \str{postalCode}: \str{NW53HL} ~\}~\}\\
\end{array}
\end{equation*}
\caption{\small{Example of a Schema.org annotation using a JSON encoding (it is worth noting 
that Schema.org also supports RDF).}}
\label{fig:schema}
\vspace{-1em}
\end{figure}

As an example, Figure~\ref{fig:schema} shows a Schema.org description of a place.
The \str{@context} attribute defines a namespace of a schema that defines the available
entities. The default namespace, used here, includes two entities that we use in this 
example, namely Place and PostalAddress.
